Verifying Demonstrations

### 2019-10-21 paper/DB-anon-cred.tex
Minor cosmetic edits
Improves TF resistance proof

\daniel{Still intuition, we need the formal definition of security above.}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
\end{theorem}

@@

  Now \(\S\) will use \(\adv\) in a simulation.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge uniformly randomly.
  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
  independent (uniformly random), the help provided by the prover must be 
  independent of the chosen challenge.
  Thus \(\S\) will provide the same help as before.

  When \(S\) has the second response it can compute the secret of the prover 
  and thus authenticate to the verifier with probability \(p_{\S} = 1\) in any 
  successive session.
  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
\end{proof}

>>>>

\daniel{Work in progress!}
\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
\end{theorem}

@@

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
  independent (uniformly random), the help provided by the prover must be 
  independent of the chosen challenge.

  Now \(\adv\) will provide a correct response with \(\frac{1}{m^n}+\epsilon\) 
  probability.
  When \(S\) has the correct response it can compute the secret of the prover 
  using the two known correct responses and thus authenticate to the verifier 
  with probability \(p_{\S} = 1\) in any successive session.
  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
\end{proof}
